Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-09 latex-acm/cloneoverflow.tex
Updated latex

The classification scheme is described in \Cref{tab:classification_scheme} and the classification results are shown in \Cref{tab:classification_good_o}. We have manually investigated all of the 2,261 good-match ones reported by agreement of four different Simian and NiCad settings.  However, for the ok-match, we could not investigate all of the 23,868 pairs manually.  According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number, 2225 (99.87\%), of false positive results (category D, E, and F). Thus, we decided to leave them out of the manual investigation of ok-match pairs. There are totally 608 ok-match pairs that were investigated. The 39 true positive pairs found are combinations of 8 unique Stack Overflow fragments, and 9 unique Qualitas Java files from 6 different projects.

>>>>

The classification scheme is described in \Cref{tab:classification_scheme} and the classification results are shown in \Cref{tab:classification_good_o}. We have manually investigated all of the 2,261 good-match clone pairs.  However, for the ok-match clone pairs, we could not feasibly investigate 23,868 pairs manually.  According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,225 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs). We thus decided to leave them out of the manual investigation. There are totally 4,625 ok-match pairs that were investigated. The 49 true positive pairs found are combinations of 12 unique Stack Overflow fragments, and 14 unique Qualitas Java files from 10 different projects.
